Equation-of-state insensitive relations after GW170817

### 2019-02-27 paper/bin-love-after-gw170817.tex
minor change

We begin by testing our Fisher analysis (with an IMRD + 6PN waveform injection) against a simulated event identical to GW170817 with O2 detector sensitivity~\cite{aLIGO}. Because only 1 event was detected, we use $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes. Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817. We used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\tilde\Lambda=395$ (Corresponding to GW170817), and $0$ for the remaining parameters. We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}. The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO~\cite{TheLIGOScientific:2017qsa,Abbott2018}

@@

Next, we consider events similar to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector. The latter is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector. 
Similar to before, we used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\lambda_0=150$, $\lambda_1=-213$ (corresponding to the GW170817), and $0$ for the remaining parameters.
Also as before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
The process we use to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
From this, we determine if and when the statistical uncertainties associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using the binary Love relations.

>>>>

We begin by testing our Fisher analysis (with an IMRD + 6PN waveform injection) against a simulated event identical to GW170817 with O2 detector sensitivity~\cite{aLIGO}. Because only 1 event was detected, we use $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes. Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817. We used fiducial template parameter values of $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\tilde\Lambda=395$ (Corresponding to GW170817), and $0$ for the remaining parameters. We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}. The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO~\cite{TheLIGOScientific:2017qsa,Abbott2018}

@@

Next, we consider events similar to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector. The latter is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector. 
Similar to before, we used fiducial template parameter values of $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\lambda_0=150$, $\lambda_1=-213$ (corresponding to the GW170817), and $0$ for the remaining parameters.
Also as before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
The process we use to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
From this, we determine if and when the statistical uncertainties associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using the binary Love relations.
